---
title: "Overview"
output: blogdown::html_page
menu:
  docs:
    parent: "schedule"
weight: 200
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Week 1

**Get your feet wet**

- Why psychologists program
- The anatomy of code and code editors

## Week 2

**Be the boss of columns**

- Data types
- Logical and relational operators
- Tidy dataframe manipulation
- Troubleshooting as an experimentation skill

Due: Problem set 1

## Week 3

**Dirty data done dirt cheap**

- Joining data
- Reshaping data
- Dealing with irregular data

Due: Problem set 2

## Week 4

**_Writing_ code**

- R scripts and R Markdown
- Scripting hygiene
- Debugging in the code editor

Due: Problem set 3

## Week 5

**Big data: the good, the bad, the ugly**

- Reading and writing data into and out of R
- Working with behavioral data from the internet
- The pros and cons of "big data"

Due: Problem set 4

## Week 6

**An eye on data visualization**

- The grammar of graphics
- Graphs as communication devices

Due: Problem set 5

```{r}
blogdown::shortcode_html(.name = "alert",
                         icon = "💻",
                         .content = "Midterm take-home exam open this week")
```

## Week 7

**The medium is the (scientific) message**

- Graph customization
- Visual communication best practices

Due: Midterm exam

## Week 8

**Putting the stats in statistical computing**

- Working with regression models

Due: Problem set 6

## Week 9

**Putting _more_ stats in statistical computing**

- Simulating data
- Power analysis

Due: Problem set 7

## Week 10

**Capital-P Programming**

- Nested data and other list columns
- Writing functions
- Advanced debugging

Due: Problem set 8

## Week 11

**Reproducibility: what is it good for?**

- Preparing and documenting code and data for sharing
- Code testing

Due: Problem set 9

## Week 12

**Stop, collaborate, and listen**

- Version control with git
- Peer reviewing code effectively and respectfully

Due: Problem set 10

## Week 13

**Give them the old razzle dazzle**

- Formatting and publishing analysis write-ups
- Creating interactive plots and tables

Due: Problem set 11

```{r}
blogdown::shortcode_html(.name = "alert",
                         icon = "💻",
                         .content = "Final take-home exam open this week")
```

## Week 14

**People's choice**

- Student-selected topics

Due: Final exam
