---
title: "Course policies"
output: blogdown::html_page
menu:
  docs:
    parent: "syllabus"
weight: 150
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Fostering an inclusive classroom

My aim is for all of us to foster a learning environment that both supports a diversity of backgrounds and experiences and encourages you to expand your understanding. Please contact me with any concerns or suggestions you may have to better address your learning needs and to improve the effectiveness of this course.

```{r}
blogdown::shortcode_html(.name = "alert", .content = "Form statement re campus disability accommodations office")
```

## Health & well-being

Many of us have periods in which our mental health and well-being suffer. We urge you to take care of yourselves and each other. 

We are in this together. Please prioritize your mental health and well-being, reach out for help if you need it, and, if you see others who may be struggling, please make sure they know how to find the support they need.

There are many resources available to you both within our classroom community and for the whole university:

```{r}
blogdown::shortcode_html(.name = "alert", .content = "Form statement from university re: campus physical and mental health services")
```

## Ensuring academic integrity

```{r}
blogdown::shortcode_html(.name = "alert", .content = "Form statement from university re: academic integrity")
```
